Supplemental Material for ``Assessing United States county-level exposure for research on tropical cyclones and human health"

### 2020-09-10 ehp_revision/response_to_reviewers.Rmd

Thank you for this suggestion. We have changed the wording in this sentence:

> **Text in revised manuscript (relevant change in bold):**
"In many cases, these studies analyze multi-year, multi-community data, allowing
them to estimate average associations over many disasters and to explore how a
disaster's characteristics, or the characteristics of the **affected
communities**, modify associated health risks (e.g., Anderson and Bell 2010; Son
et al. 2012; Liu et al. 2017)."

We also used the word "Hits per county per decade" in the legend for Figure 5 in
the main text (reproduced in this response document as Figure \@ref(fig:fig5))
and Figure S3 of the Supplemental Material. We have revised the wording in these
figures to "Exposures per county per decade".

```{r fig5, fig.cap="Reproduction of Figure 5 from the original manuscript (left) and revised version in the resubmitted manuscript (right). In the revised version, the figure legend was changed from '\\textbf{Hits} per county per decade' to '\\textbf{Exposures} per county per decade' (bold used to highlight change).}", fig.show = "hold", out.width="40%", fig.align = "center"}
include_graphics("../figures/averageexposureonly.pdf")
include_graphics("figures/averageexposureonly.pdf")
```

@@

\begin{quotation}
\noindent
\textit{"For another set of tropical cyclones (e.g., Ernesto in 2006, and Bertha
in 1996, Isabel in 2003), there was moderate to good agreement for pairwise
combinations of distance, rain, and wind, but poor agreement for other
combinations of metrics, while for another set of storms (e.g., Matthew in 2004
and Katrina in 2005), there was moderate to good agreement between distance and
rain."}
\end{quotation}

\end{shaded}

**Response:**

We have included a measurement of agreement between different hazard-based
exposure metrics for two reasons. First, while we agree with the reviewer that a
direct measurement is always preferable to a proxy, there are still some studies
that, when assessing tropical cyclone exposure based on measurements of physical
hazards, use a single hazard for this exposure assessment. We are most familar
with cases where a wind-based metric has been the focus in these cases (e.g.,
@sun2020tropical, @grabich2015measuring). Therefore, sometimes might not be
ideal, it is done in practice. To interpret these studies, it is helpful to
understand the degree to which this single-hazard metric agrees with exposure
patterns for other hazards. If the exposure patterns are in strong agreement for
all hazards, then these studies could be interpreted as estimating risk
associated with exposure to tropical cyclones as a whole. If the exposure
patterns are in low to moderate agreement, then these studies should be
interpreted instead as estimating the risk associated with that specific storm
hazard, but not for all storm hazards. In this case, if the agreement is
moderate, though, there is a chance of confounding from other storm hazards
(i.e., an association that is attributed to one storm hazard was actually the
result of another that was not included in the model). In this paper, we present
measurements of agreement across four hazard-based exposure metrics that can
provide insight on these points.

Second (and related), epidemiologists need to understand how these exposure
measurements agree to help in planning studies and statistical approaches to
interpreting the resulting data. In this sense, "agreement" is providing a
measure similar to correlation for continuous variables; our choice of agreement
with the binary exposure classifications reflects the more common use of binary
classifications for most tropical cyclone epidemiology to date.

There are several things that an epidemiologist could derive from these results
to help in designing a study and the associated statistical analysis. First, the
results we present can help epidemiologists determine if they can use a single
metric of tropical cyclone exposure in their studies, or if they need to instead
consider tropical cyclones as a mixture of hazards. There are a number of
practical reasons to use a single exposure metric, if doing so is reasonable
(even if it's not conceptually ideal). While there have been advances in methods
for mixtures research in environmental epidemiology, these are often more
complex than the long-used and well-developed methods for studying single
exposures, and many epidemiologists are much more comfortable with methods for
single exposures compared to methods for mixtures. Further, it can be easier to
communicate results from single-exposure studies clearly and succinctly.
Therefore, if there is a reasonable way to measure exposure with a single
metric, there are practical reasons that recommend that approach, even if
conceptually it might be preferable to incorporate separate hazards.

If, at the county level, there were strong agreement among exposure patterns for
the different tropical cyclone hazards we considered, it might have been
reasonable to recommend the use of a single hazard-based metric as a proxy for
exposure to all storm hazards in epidemiological studies for practical reasons.
We found that this is almost never the case, although there are a few select
storms (like Hurricane Floyd in 1999) where such an approach might be
justifiable. Most atmospheric scientists would not be surprised by our findings
about this disagreement in exposure patterns for different tropical cyclone
hazards, but this finding is not as self-evident for environmental
epidemiologists. Based on a recent conference of the Interational Society for
Environmental Epidemiology, for example, there are a number of environmental
epidemiologists with backgrounds focused on methods and other ambient exposures
(e.g., air pollution, heat) who are beginning to include tropical cyclones as an
exposure of interest in their studies, and we believe these results would be
novel and useful to many of them.

Second, in cases where it is clear that a mixture approach is necessary, these
results can help in understanding what challenges might arise in statistical
analysis. While one approach to including several hazards could be to create an
index of tropical cyclone exposure by taking a weighted sum of all hazards, for
most health outcomes it is unclear *a priori* what the weight for each hazard
should be in such an index, and so it will often be preferable to discover those
weights from the data by fitting a statistical model that includes each hazard
as an independent variable. In these cases, strong correlation (or agreement, in
the case of binary exposures) among separate independent variables can create
both numerical issues (e.g., variance inflation from multicollinearity) and
difficulties in interpretation (e.g., difficulty infering the role of specific
hazards and separating the influece of each). If an epidemiologist has a good
understanding of these patterns in their data, he or she can adopt methods that
address potential issues, including using matching-based study designs to create
a subset of storms to study in which separate hazards are well-distinguished
from each other, incorporation of dimension-reduction methods like principal
components analysis, or shrinkage techniques that allow for a small amount of
bias in estimation of associations in return for reducing problems from
collinearity (e.g., ridge regression) [@leal2012multicollinearity;
@schisterman2017collinearity].

The reviewer makes a good point that it is important for us to clarify our
motivation for measuring agreement between the hazard-based metrics, as well as
to show readers how our results from these measures can be used to help in
designing studies and planning statistical analysis for tropical cyclone
epidemiology. We have added text to the manuscript on these points:

> "Finally, we investigated how well exposure assessment agreed across these
metrics. **These results can help epidemiologists answer several key questions as
they interpret previous research and design new studies. For example, if a
single storm hazard has been used to measure exposure in an epidemiological
study, can the result be interpreted as an association with tropical cyclone
exposure in general, or should it be limited to represent an association with
that specific storm hazard? If a study investigates the association between a
single storm hazard and a health outcome, could this estimate be confounded by
other storm hazards? When planning a new study that will incorporate several
storm hazards in a mixtures approach, will there likely be numerical problems in
fitting the model from multicollinearity, or difficulties in disentangling the
role of separate hazards?**"

@@

\medskip

\begin{shaded}
\textbf{R2 Comment 4:}
Table 2: This is another confusing table. Not sure what compared here. The
second column is a mean \# of exposed counties over years and the third column
seems like showing single storm with the max \# of exposed counties. Not sure
what info I should digest from this table.
\end{shaded}

**Response:**

We included this table with the intent that these results can help
epidemiologists who are planning new single-storm or multi-year studies of
tropical cyclones and associated health risks. For planning a multi-year study,
it is helpful to know how many exposures the study might incorporate, as this
can help in giving a general idea of whether the study might have adequate
statistical power to investigate a certain research question. Similarly, for
single-storm studies, it is helpful to know how widespread exposure can be for a
specific hazard during a very large storm. This table provides some basic
summaries of the extent of exposure to different tropical cyclone hazards, both
on average for the storms in the study and also for those storms that were most
extensive.

@@

\begin{shaded}
\textbf{R3 Comment 7:}
Figure 3: The x-axis refers to one of the two wind data sources as "Extended
Best Tracks." Is this the same thing as the wind radii dataset described in the
text? Is so, I suggest clarifying this in the figure label.
\end{shaded}

**Response:**

Yes, it is the same. We have revised the x-axis on the figure to clarify that
the comparison is based on the wind radii dataset described in the text, as
requested. The original and revised versions of Figure 3 of the manuscript are
reproduced in this response document as Figure \@ref(fig:fig3).

```{r fig3, fig.cap="Reproduction of Figure 3 from the original manuscript (left) and revised version in the resubmitted manuscript (right). In the revised version, the x-axis has been labelled to clarify that this axis is showing results based on the wind radii dataset described in the text, in response to Reviewer 3's Comment 7. The revised version also uses a more focused range for the x axis, as requested in EHP's Request 1.", fig.show = "hold", out.width="50%"}
include_graphics("../figures/windcomparison.pdf")
include_graphics("figures/windcomparison.pdf")
```

### 2020-09-10 ehp_revision/writing/ehp_methods.tex
Work some more on revisions

Finally, we investigated how well exposure assessment agreed across 
these metrics. For each storm we investigated the degree to which the 
set of counties assessed as exposed based on one metric overlapped with the set
assessed as exposed based on each other metric, including a metric that used
distance of a county from the storm track as a proxy for exposure to storm hazards. 
We calculated the within-storm
Jaccard index ($J_s$)~\parencite{jaccard1901distribution, jaccard1908nouvelles} between
each pair of exposure metrics. This measures similarity
between two metrics ($X_{1,s}$ and~$X_{2,s}$) for tropical cyclone~$s$ as the
proportion of counties in which both of the metrics classify the county as
exposed out of all counties classified as exposed by at least one of the
metrics:

>>>>

Finally, we investigated how well exposure assessment agreed across these
metrics. \textbf{These results can help epidemiologists answer several key
questions as they interpret previous research and design new studies. For
example, if a single storm hazard has been used to measure exposure in an
epidemiological study, can the result be interpreted as an association with
tropical cyclone exposure in general, or should it be limited to represent an
association with that specific storm hazard? If a study investigates the
association between a single storm hazard and a health outcome, could this
estimate be confounded by other storm hazards? When planning a new study that
will incorporate several storm hazards in a mixtures approach, will there
likely be numerical problems in fitting the model from multicollinearity, or
difficulties in disentangling the role of separate hazards?}

For each storm we investigated the degree to which the set of counties assessed
as exposed based on one metric overlapped with the set assessed as exposed
based on each other metric, including a metric that used distance of a county
from the storm track as a proxy for exposure to storm hazards.  We calculated
the within-storm Jaccard index ($J_s$)~\parencite{jaccard1901distribution,
jaccard1908nouvelles} between each pair of exposure metrics. This measures
similarity between two metrics ($X_{1,s}$ and~$X_{2,s}$) for tropical
cyclone~$s$ as the proportion of counties in which both of the metrics classify
the county as exposed out of all counties classified as exposed by at least one
of the metrics:
